|

### 2021-05-26 article/resubmission.Rmd

Agrupamentos possíveis (agrupar só os que batem no nosso resultado): 
- métodos (esse bate)
- institutional design
- electoral system

Introduction:
1 - como está originalmente.
2 - in this letter we run a meta analysis papapá, explicando o que fazemos no texto e o que encontramos.
3 - resultados são all over the place: e a literatura ja sabia que eram all over the place (vira revisãozinha de literatura).
4 - agora a gente diz o que nossos resultados representam pros estudos: no caso, podemos concluir que os autores x, y, z foram pela linha correta.

Results: Colocar resultados da meta-regressão completa na última tabela.

Discussion:
1 - ok
2 - ok, só corrigir
3 - como nossos resultados "resolvem" as questões da teoria
a linha que avalia o desenho institucional está certa dessa forma.
sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, nós podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
4 - ultimo paragrafo vira o que é o terceiro. uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. More recently, the discussion of the "law of $1/n$" has surpassed its original formulation. Specifically, the theory meant to explain distributive behavior of US district legislators under majoritarian electoral rules. It has since then been applied to a number of contexts whose political features do not fit into what @weingast1981political had theorized.

Colocar aqui no final desse paragrafo "in this paper we..."

The mechanism behind $1/n$ is incumbents' choice of redistributive strategy to optimize chances of reelection. The _norm of universalism_, by which all legislators pass each other's bills, guarantees that all representatives are allotted an amount of resources to cater projects to their voters. @crowley2019law contests this scenario where coordination costs are minimal, aiming at solving the discrepancies in previous works. The literature finds that a number of players and features can override the $1/n$ effect by posing checks to legislative activity and altering coordination costs. First, shifts in the level of intra or intergovernmental competition based on district homogeneity, supermajority rules, the size of coalitions, and even gerrymandering have been shown to interfere with the effect of chamber size on spending [@bjedov; @crain1999; @crowley2015; @gilligan2006; @lee2015; @mukherjee2003; @pecorino2018]. Second, we must take into account players who function as institutional checks, such as strong executives who take on legislative duties, other deliberative chambers, or spending limits, who also directly influence legislators' access to common pool funds [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.

Grudar aqui no final o início do pargrafo seguinte, retirando toda a descrição de ~como conduzimos a meta~, sem descrição das variaveis e modelos.

XXXXXX Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy]. XXXXXXXX

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber, its natural logarithm, and the number of members
in the upper chamber. We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on
public spending. However, the meta-regressions suggest that our study sample
has high levels of heterogeneity, and effects differ substantially according to
study specifications. While papers that employ
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".
Additionally, we find that non-majoritarian voting systems decrease government
spending as a percentage of GDP, which is also evidence against the theoretical
expectations of the "law of $1/n$", and they do not have a relevant impact on
the other measures of public expenditure. However, unicameralism strongly supports the positive effect predicted by the original theory. This result is contradictory to the rest of our findings, even if unicameral cases mostly reflect the very specific framework under which the theory developed (loosely checked local governments). In summary, our analysis does not
provide robust support for the theory as originally conceived, and causal
inference models suggest that larger legislatures are associated with lower
public spending.

@@

We compiled our final sample of papers from two large collections of records. In the first round of the search, we scraped three large academic databases (Scopus, Microsoft Academic, and Google Scholar) for studies that cited \citet{weingast1981political}. We developed exclusion criteria to select only articles written in the English language that used quantitative methods to investigate the relationship between legislature size and public spending.\footnote{Please refer to section C in the Supplementary Material for a more detailed description of the selection procedure, including a PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow diagram \citet{liberati2009prisma} showing the number of resulting papers after each review step.} Upon restricting the sample, we identified which were the most commonly used measurements to operationalise these variables of interest, and adopted them as our key explanatory variables.\footnote{As meta-analysis requires a single estimate per observation, we excluded articles that use interaction terms or quadratic specifications of our independent variables.} We found those to be public expenditure as a share of GDP, public expenditure per capita, and the natural logarithm of public expenditure per capita as dependent variables. As independent variables, most studies use lower chamber size, upper chamber size, and the natural logarithm of lower chamber size.\footnote{There are a few important nuances to the coding of these variables. Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as key explanatory variables. We did not find any articles that used the natural logarithm of upper chamber size.} In the second round, we selected key terms to conduct a broader search of the literature on Google Scholar and applied the same eligibility criteria. Combined, the two searches produced a dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March, 2021. Table \ref{tab:papers} contains the full list of articles from which we drew data.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Note:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Note:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Note:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, as the first paper to apply it was published in 2012.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) estimation method; 4) institutional design; 5) electoral system.
Since the literature on the "law of $1/n$" is notably diverse, we included only moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

One of the assumptions in meta-analyses is effect size independence. In our sample of coefficients, we have sources of independence within and between articles, and we solve them using two distinct procedures. Since authors often submit their data to different models, each paper reports several effect sizes using the same variables. To reduce the impact of multicollinearity,
we produce and analyse two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \footnote{The papers that used more than one dependent or independent variable of interest were \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop, ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers. In both restricted and extended sets, a number of papers use overlapping data -- from the same constituency, using the same variables, during the same time period.\footnote{For instance, 8 papers used U.S. State data from both the U.S. Census Bureau’s “Annual Survey of State and Local Government Finances” and The Council of State Government’s Book of the
States.} We correct this source of bias by employing a multilevel random effects model [@cheung2014modeling], grouping redundant(?) studies. Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. We discuss eventual differences in the next section.

@@

>>>>

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Recent research has further
questioned the validity of the "law of $1/n$". Since the wide range of empirical tests has produced conflicting results, scholars began to target the theoretical foundations of the law. Authors such as @crowley2019law and @pecorino2018supermajority accurately point out that collective action problems have been overlooked, but their expanded models cannot account for all the institutional variation previous studies explore.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

We believe the scrutiny of the law expanded its initial scope in two directions. One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards. They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S. majoritarian local legislatures, for which the law was conceived. Another sector of the scholarship overrides this institutional context. They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc. produce more nuanced results. For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative. While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness. We address all of these developments in this study. We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.

Aggregate results show that legislative size has no significant impact on
public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications. In the broadest aggregation models, unicameralism supports the positive effect predicted by the 
law of $1/n$. Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework. It also indirectly endorses studies that find odd results in bicameralism. As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal]. 
Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.

The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods. While papers that employ conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
with previous findings that lend partial support to the law of $1/n$ 
[@chen2007law; @crowley2015local; @primo2006stop]. An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results. Overall, our analysis does not
provide robust support for the theory as originally conceived.

@@

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Notre:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Journals:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Methods:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Dependent Variables:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference designs,
such as instrumental variables and regression discontinuity models.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables of interest are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
included only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material.

@@

Resumir resultados das meta-análises.
Incluir regressões com todos os coeficientes na tabela de meta-regressions.
Incluir frases com "highlights" na sub-seção de meta-regressions.
Trocar parágrafo introdutório e o de binomial z-tests pela nova versão do Danilo (que não subiu pro repo).
